Analysis : exp231 analysis

### 2018-12-08 resistingrhythm/analysis/exp229.Rmd
Plot play

```{r, message=FALSE}
library(tidyverse)
library(gridExtra)
library(grid)
library(ggpubr)
library(cowplot)

@@

```{r, fig.width=1.5, fig.height=1.2}
null_rate <- mean(filter(results229, osc_rate == "0")$rate_k)
results229 %>% 
  filter(osc_rate != "0") %>%
  ggplot(aes(x=frac_tau_h, y=rate_k)) +
    geom_boxplot() +
    theme_classic2() +
    scale_color_brewer(palette="PuOr", direction=-1) +
    labs(x="Frac. tau_h", y="Pop. rate") +
    theme(legend.position = "none")
```

```{r}
results229 %>% 
  filter(osc_rate == "2") %>% 
  ggplot(aes(x=freq, y=rate_k, color=frac_tau_h)) +
  geom_boxplot() +
  theme_classic2() +
  scale_color_brewer(palette="BrBG", direction=-1) +
  labs(x="Frequency (Hz)", y="Pop. rate") 
```

```{r}
results229 %>% 
  filter(osc_rate != "0") %>% 
  ggplot(aes(x=osc_rate, y=rate_k, color=frac_tau_h)) +
  geom_boxplot() +
  theme_classic2() +
  scale_color_brewer(palette="BrBG", direction=-1) +
  labs(x="Osc. rate", y="Pop. rate") 
```

>>>>

```{r, message=FALSE}
library(ggplot2)
library(dplyr)
library(magrittr)
library(readr)
library(gridExtra)
library(grid)
library(ggpubr)
library(cowplot)

@@

```{r, fig.width=1.4, fig.height=0.8}
# null_rate <- mean(filter(results229, osc_rate == "0")$rate_k)
results229 %>% 
  ggplot(aes(x=frac_tau_h, y=rate_k)) +
    geom_boxplot() +
    theme_classic2() +
    labs(x="Frac. tau_h", y="Pop. rate") +
    theme(legend.position = "right") 
```

```{r, fig.width=2.2, fig.height=1.2}
null_rate <- mean(filter(results229, osc_rate == "0")$rate_k)
results229 %>% 
  filter(osc_)
  ggplot(aes(x=frac_tau_h, y=rate_k - null_rate, color=osc_rate)) +
    geom_jitter(size=0.01, width=.2) +
    theme_classic2() +
    scale_color_manual(values=c("grey", "firebrick1", "firebrick3", "firebrick4")) +
    labs(x="Frac. tau_h", y="Pop. rate") +
    theme(legend.position = "right") 
```

```{r, fig.width=1.2, fig.height=0.6}
results229 %>% 
  # filter(osc_rate == "4") %>%
  ggplot(aes(x=freq, y=rate_k, color=as.numeric(frac_tau_h), group=interaction(freq, frac_tau_h))) +
  geom_jitter(size=0.02, width=.2, alpha=0.5, outlier.colour = NA) +
  # geom_boxplot() +
  # geom_jitter() +
  theme_classic2() +
  scale_color_gradient(high="plum4", low="lightgrey") +
  labs(x="Frequency (Hz)", y="Pop. rate") +
  theme(legend.position = "none")
```

```{r fig.width=1, fig.height=0.85}
results229 %>% 
  # filter(osc_rate != "0") %>%
  # filter(freq == "8") %>%
  ggplot(aes(x=osc_rate, y=rate_k, 
             color=as.numeric(frac_tau_h), group=interaction(frac_tau_h, osc_rate))) +
  geom_jitter(size=0.02, width=.2, outlier.colour = NA) +
  theme_pubr() +
  scale_color_gradient(high="plum4", low="lightgrey") +
  labs(x="Osc. rate", y="Pop. rate") +
  theme(legend.position = "none")
```

### 2018-12-08 resistingrhythm/analysis/exp231.Rmd
Plot play

```{r, fig.width=2.2, fig.height=1.1}
rbind(results231, results232) %>% 
  ggplot(aes(x=frac_tau_h, y=rate_k, color=homeo, group=interaction(homeo, frac_tau_h))) +
  geom_boxplot() +
  scale_color_manual(values=c("black", "grey"), name="") 
```

>>>>

```{r, fig.width=2.2, fig.height=1.1}
rbind(results231, results232) %>% 
  ggplot(aes(x=frac_tau_h, y=rate_k, color=homeo, group=interaction(homeo, frac_tau_h))) +
  geom_boxplot(size=0.6) +
  scale_color_manual(values=c("black", "grey"), name="") 
```
